{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
fixed structure
removed placeholder for abstract
cite full version of the paper correctly

{\bf Here comes the abstract!}

@@

The proof that this definition fulfills the properties from section \ref{sec:soundness} and all other
proofs can be found in the full version of the paper. \todo{cite the full version}

@@

\section{Related Work}
\label{sec:relatedwork}
\section{Conclusion \& Outlook}
\label{sec:conclusion}

>>>>

@@

The proof that this definition fulfills the properties from section \ref{sec:soundness} and all other
proofs can be found in \cite{Barthe09}.

@@

\section{Comparison with other aproaches/further work}
\label{sec:furtherwork}
